Energy-constrained wireless networks are conventionally powered by batteries. However, limited operation time and high cost in recharging or replacement have become bottlenecks for smart networks as Internet-of-Things (IoT). As a promising solution, Energy Harvesting (EH) from the ambient environment can potentially provide perpetual power to the devices. Compared with other renewable resources as solar, wind and water, Radio-Frequency (RF) waves typically contain less energy and are more suitable for low-power applications as Wireless Sensor Network (WSN). Recently, the significant reduction in power requirements of chips and processors brings more attention to Wireless Power Transfer (WPT) in both academia and industry \cite{R.Varshney2008, Grover2010, Zhang2013, Hui2014, Krikidis2014, Valenta2014, Boshkovska2015, Ding2015, Costanzo2016, Clerckx2018a}.

On the other hand, RF radiation has been a medium for Wireless Information Transfer (WIT) for more than a century. Naturally, a unified design of Wireless Information and Power transmission (WIPT) is expected to be a prominent solution to power billions of mobile devices while keeping them connected. \cite{R.Varshney2008} first defined a nonlinear concave capacity-energy function and investigated the tradeoff for typical binary channels and a flat additive white Gaussian noise (AWGN) channel with amplitude-constrained inputs. It was extended to frequency-selective channel in \cite{Grover2010}. However, both works were based on the ideal case that information decoding (ID) and EH can be performed individually on the same received signal. In \cite{Zhang2013}, the authors proposed two practical co-located receiver designs named \textit{time switching} (PS) that switches between ID and EH and \textit{power splitting} (TS) that splits the received power into two separate streams. It was then demonstrated in \cite{Zhou2013a} that TS can guarantee the same rate as conventional Time-Division Multiple Access (TDMA) while providing considerable power. In comparison, PS may lead to higher rate when the demand on power is sufficiently high. A further research \cite{Liu2013} enabled dynamic power splitting that adjusts the power split ratio based on the channel state information (CSI), and proposed a suboptimal low-complexity \textit{antenna switching} scheme. Nevertheless, the literatures above are mostly based on an oversimplified linear harvester model. To accurately characterize the behavior of the rectenna, \cite{Clerckx2016} derived a tractable nonlinear model and performed an adaptive multisine waveform design accordingly. Realistic simulations showed significant gains in harvested power and stressed the importance of modelling rectifier nonlinearity in wireless system design. The work was extended to multi-input single-output (MISO) WIPT in \cite{Clerckx2018} where a superposition of multicarrier modulated and unmodulated waveform was optimized as a function of CSI under transmit power budget. It suggested the rectifier nonlinearity can lead to a larger rate-energy (R-E) region and favours a different waveform, modulation and input distribution. In another perspective, a learning approach \cite{Varasteh2018} modelled the transmitter and receiver as deep neural networks (NN) and jointly optimized signal encoding with network parameters. Constellations showed that the offset of the power symbol is positively correlated to the power demand, while the information symbols are symmetrically located around the origin. The pattern confirmed a unmodulated waveform is beneficial to increase the harvested power in \cite{Clerckx2018}.
